### 2014-07-24 doc/thesis/cases.tex
Removing the typyping of the debug library
Fixing the type of table.sort

\begin{enumerate}
\item table.concat (list [, sep [, i [, j]]]) :
\begin{verbatim}
({string|number}, string?, number?, number?) -> (string)
\end{verbatim}
Category 1.
\\
I guess the proper type should be:
\begin{verbatim}
({string|number}) |
({string|number}, string) |
({string|number}, string, number?) -> (string)
\end{verbatim}
\item table.insert (list, [pos,] value) :
\begin{verbatim}
({any}, any) -> ()
\end{verbatim}
Category 2.
\\
This function does not accept/discard extra parameters.
Perhaps due to the fact that the parameter \textbf{pos} is optional.
If \textbf{value} is $\TopStar$, the function inserts \textbf{pos}
in the \textbf{list}, that is, the input type is
\texttt{(\{any\}, any) -> ()}.
If \textbf{value} is $\Nil$, the function does not insert \textbf{pos}
in the \textbf{list}, that is, the input type is
\texttt{(\{any\}, number, any) -> ()},
but the element is not inserted in the list because \textbf{value}
is actually $\Nil$.
I guess the proper type should be:
\begin{verbatim}
({any}, any) | ({any}, number, any) -> ()
\end{verbatim}
\item table.pack (···) :
\begin{verbatim}
(any*) -> ({number:any, "n":number})
\end{verbatim}
Category 2.
\\
Even though \textbf{table.pack} gets any number of parameters of
any type, the $\Nil$ type generates a hole in the returned table.
\item table.remove (list [, pos]) :
\begin{verbatim}
({any}, number?) -> (any)
\end{verbatim}
Category 2.
\\
The return type depends on the type of the element that is removed
from the list.
\item table.sort (list [, comp]) :
\begin{verbatim}
({any}, any?) -> ()
\end{verbatim}
Category 2.
\\
The proper type should be:
\begin{verbatim}
({any}, (any, any) -> (boolean)?) -> ()
\end{verbatim}
But there is a syntactic conflict for defining optional function types
that should be fixed in the parser.
\item table.unpack (list [, i [, j]]) :
\begin{verbatim}
({any}, number?, number?) -> (any*)
\end{verbatim}
Category 2.
\\
The return type depends on the type of the elements that are stored in
the list.
I guess the proper type should be:
\begin{verbatim}
({any}) | ({any}, number, number?) -> (any*)
\end{verbatim}
\end{enumerate}

@@

\begin{enumerate}
\item os.clock () :
\begin{verbatim}
() -> (number)
\end{verbatim}
Category 1.
\item os.date ([format [, time]]) :
\begin{verbatim}
(string?, number?) -> (string) |
                      ({"year":number, "month":number, "day":number,
                        "hour":number, "min":number, "sec":number,
                        "wday":number, "yday":number, "isdst":boolean})
\end{verbatim}
Category 1.
\\
Returns a table when \textbf{format} contains ``\textbf{*t}''.
I guess the proper type should be:
\begin{verbatim}
() | (string) | (string, number?) -> (string) |
                      ({"year":number, "month":number, "day":number,
                        "hour":number, "min":number, "sec":number,
                        "wday":number, "yday":number, "isdst":boolean})
\end{verbatim}
\item os.difftime (t2, t1) :
\begin{verbatim}
(number, number?) -> (number)
\end{verbatim}
Category 1.
\\
Returns \textbf{t2} when \textbf{t1} is $\Nil$.
\item os.execute ([command]) :
\begin{verbatim}
(string?) -> (boolean) | (true?, string, number)
\end{verbatim}
Category 3.
\\
Returns just a Boolean when \textbf{command} is $\Nil$.
This Boolean means whether there is a shell available.
Returns \texttt{(true, string, number)} when
\textbf{command} terminated successfully.
Returns \texttt{(nil, string, number)} when
\textbf{command} did not terminate successfully.
\item os.exit ([code [, close]]) :
\begin{verbatim}
(boolean|number?, value?) -> ()
\end{verbatim}
Category 1.
\\
I guess the proper type should be:
\begin{verbatim}
() | (boolean|number) | (boolean|number, value?) -> ()
\end{verbatim}
\item os.getenv (varname) :
\begin{verbatim}
(string) -> (string)
\end{verbatim}
Category 1.
\item os.remove (filename) :
\begin{verbatim}
(string) -> (true) | (nil, string, number)
\end{verbatim}
Category 1.
\item os.rename (oldname, newname) :
\begin{verbatim}
(string) -> (true) | (nil, string, number)
\end{verbatim}
Category 1.
\item os.setlocale (locale [, category]) :
\begin{verbatim}
(string?, "all"|"collate"|"ctype"|"monetary"|"numeric"|"time"|nil) ->
(string) | (nil)
\end{verbatim}
Category 3?
\\
The return type depends on the input type:
\begin{verbatim}
() -> (string)
(string, "all"|"collate"|"ctype"|"monetary"|"numeric"|"time"|nil) ->
(string) | (nil)
\end{verbatim}
\item os.time ([table]) :
\begin{verbatim}
({"year":number, "month":number, "day":number,
  "hour":number?, "min":number?, "sec":number?,
  "wday":number?, "yday":number?, "isdst":boolean?}?) -> (number)
\end{verbatim}
Category 1.
\item os.tmpname () :
\begin{verbatim}
() -> (string)
\end{verbatim}
Category 1.
\end{enumerate}

@@

\begin{enumerate}
\item debug.debug () : ?
\item debug.gethook ([thread]) : ?
\item debug.getinfo ([thread,] f [, what]) : ?
\item debug.getlocal ([thread,] f, local) : ?
\item debug.getmetatable (value) : ?
\item debug.getregistry () : ?
\item debug.getupvalue (f, up) : ?
\item debug.getuservalue (u) : ?
\item debug.sethook ([thread,] hook, mask [, count]) : ?
\item debug.setlocal ([thread,] level, local, value) : ?
\item debug.setmetatable (value, table) : ?
\item debug.setupvalue (f, up, value) : ?
\item debug.setuservalue (udata, value) : ?
\item debug.traceback ([thread,] [message [, level]]) : ?
\item debug.upvalueid (f, n) : ?
\item debug.upvaluejoin (f1, n1, f2, n2) : ?
\end{enumerate}

>>>>

\begin{enumerate}
\item table.concat (list [, sep [, i [, j]]]) :
\begin{verbatim}
({string|number}, string?, number?, number?) -> (string)
\end{verbatim}
Category 1.
\\
I guess the proper type should be:
\begin{verbatim}
({string|number}) |
({string|number}, string) |
({string|number}, string, number?) -> (string)
\end{verbatim}
\item table.insert (list, [pos,] value) :
\begin{verbatim}
({any}, any) -> ()
\end{verbatim}
Category 2.
\\
This function does not accept/discard extra parameters.
Perhaps due to the fact that the parameter \textbf{pos} is optional.
If \textbf{value} is $\TopStar$, the function inserts \textbf{pos}
in the \textbf{list}, that is, the input type is
\texttt{(\{any\}, any) -> ()}.
If \textbf{value} is $\Nil$, the function does not insert \textbf{pos}
in the \textbf{list}, that is, the input type is
\texttt{(\{any\}, number, any) -> ()},
but the element is not inserted in the list because \textbf{value}
is actually $\Nil$.
I guess the proper type should be:
\begin{verbatim}
({any}, any) | ({any}, number, any) -> ()
\end{verbatim}
\item table.pack (···) :
\begin{verbatim}
(any*) -> ({number:any, "n":number})
\end{verbatim}
Category 2.
\\
Even though \textbf{table.pack} gets any number of parameters of
any type, the $\Nil$ type generates a hole in the returned table.
\item table.remove (list [, pos]) :
\begin{verbatim}
({any}, number?) -> (any)
\end{verbatim}
Category 2.
\\
The return type depends on the type of the element that is removed
from the list.
\item table.sort (list [, comp]) :
\begin{verbatim}
({any}, nil|(any, any) -> (boolean)) -> ()
\end{verbatim}
Category 2.
\\
Do we really need grouping?
\begin{verbatim}
({any}, [(any, any) -> (boolean)]?) -> ()
\end{verbatim}
Grouping would be useful for defining types like this:
\begin{verbatim}
([(number) -> (number)] | (string) -> (string)) -> ({string})
\end{verbatim}
But we do not have intersection types anyway.
\item table.unpack (list [, i [, j]]) :
\begin{verbatim}
({any}, number?, number?) -> (any*)
\end{verbatim}
Category 2.
\\
The return type depends on the type of the elements that are stored in
the list.
I guess the proper type should be:
\begin{verbatim}
({any}) | ({any}, number, number?) -> (any*)
\end{verbatim}
\end{enumerate}

@@

\begin{enumerate}
\item os.clock () :
\begin{verbatim}
() -> (number)
\end{verbatim}
Category 1.
\item os.date ([format [, time]]) :
\begin{verbatim}
(string?, number?) -> (string) |
                      ({"year":number, "month":number, "day":number,
                        "hour":number, "min":number, "sec":number,
                        "wday":number, "yday":number, "isdst":boolean})
\end{verbatim}
Category 1.
\\
Returns a table when \textbf{format} contains ``\textbf{*t}''.
I guess the proper type should be:
\begin{verbatim}
() | (string) | (string, number?) -> (string) |
                      ({"year":number, "month":number, "day":number,
                        "hour":number, "min":number, "sec":number,
                        "wday":number, "yday":number, "isdst":boolean})
\end{verbatim}
\item os.difftime (t2, t1) :
\begin{verbatim}
(number, number?) -> (number)
\end{verbatim}
Category 1.
\\
Returns \textbf{t2} when \textbf{t1} is $\Nil$.
\item os.execute ([command]) :
\begin{verbatim}
(string?) -> (boolean) | (true?, string, number)
\end{verbatim}
Category 3.
\\
Returns just a Boolean when \textbf{command} is $\Nil$.
This Boolean means whether there is a shell available.
Returns \texttt{(true, string, number)} when
\textbf{command} terminated successfully.
Returns \texttt{(nil, string, number)} when
\textbf{command} did not terminate successfully.
\item os.exit ([code [, close]]) :
\begin{verbatim}
(boolean|number?, value?) -> ()
\end{verbatim}
Category 1.
\\
I guess the proper type should be:
\begin{verbatim}
() | (boolean|number) | (boolean|number, value?) -> ()
\end{verbatim}
\item os.getenv (varname) :
\begin{verbatim}
(string) -> (string?)
\end{verbatim}
Category 1.
\item os.remove (filename) :
\begin{verbatim}
(string) -> (true) | (nil, string, number)
\end{verbatim}
Category 1.
\item os.rename (oldname, newname) :
\begin{verbatim}
(string, string) -> (true) | (nil, string, number)
\end{verbatim}
Category 1.
\item os.setlocale (locale [, category]) :
\begin{verbatim}
(string?, "all"|"collate"|"ctype"|"monetary"|"numeric"|"time"|nil) ->
(string) | (nil)
\end{verbatim}
Category 3?
\\
The return type depends on the input type:
\begin{verbatim}
() -> (string)
(string, "all"|"collate"|"ctype"|"monetary"|"numeric"|"time"|nil) ->
(string) | (nil)
\end{verbatim}
\item os.time ([table]) :
\begin{verbatim}
({"year":number, "month":number, "day":number,
  "hour":number?, "min":number?, "sec":number?,
  "wday":number?, "yday":number?, "isdst":boolean?}?) -> (number)
\end{verbatim}
Category 1.
\item os.tmpname () :
\begin{verbatim}
() -> (string)
\end{verbatim}
Category 1.
\end{enumerate}

@@

We will not type the debug libraty.
